\section*{Lie groups and Lie algebras}

\begin{definition}[Lie Group]
	A \bld{Lie group} is defined to be a group object in $\mathsf{Man}$.
\end{definition}

\begin{definition}[Lie Group Homomorphism]
	A map $F \in C^\infty(G,H)$ between two Lie groups $G$ and $H$ is said to be a \bld{Lie group homomorphism}, iff $F : G \to H$ is a homomorphism.
\end{definition}

The group structure of a Lie group induces canonical maps.

\begin{definition}[Translation]
	Let $G$ be a Lie group and $g \in G$. Define $L_g,R_g \in \Diff(G)$ by
	\begin{equation*}
		L_g(h) := gh \qquad \text{and} \qquad R_g(h) := hg.
	\end{equation*}
	\noindent These maps are called \bld{left translation} and \bld{right translation by $g$}, respectively.
\end{definition}

\begin{proposition}
	Every Lie group homomorphism has constant rank.
\end{proposition}

\begin{definition}[Lie Subgroup]
	A \bld{Lie subgroup} of a Lie group $G$ is defined to be a subgroup of $G$, which is itself a Lie group and an immersed submanifold of $G$.
\end{definition}

\begin{proposition}
	Let$G$ be a Lie group and $H$ be a subgroup of $G$ such that $H$ is an embedded submanifold of $G$. Then $H$ is a Lie subgroup of $G$.
\end{proposition}

To every Lie group we can associate an algebraic object.

\begin{definition}[Lie Algebra]
	A \bld{Lie algebra} is defined to be a real vector space $\mathfrak{g}$, such that there exists a bilinear mapping
	\begin{equation*}
		[\>\cdot\>,\>\cdot\>] : \mathfrak{g} \times \mathfrak{g} \to \mathfrak{g},
	\end{equation*}
	\noindent called the \bld{Lie bracket on $\mathfrak{g}$}, such that:
	\begin{enumerate}[label=\textup{(\roman*)},leftmargin=*]
		\item \textup{(}\bld{Antisymmetry}\textup{)} $[x,y] = -[y,x]$,
		\item \textup{(}\bld{Jacobi's Identity}\textup{)} $[x,[y,z]] + [z,[x,y]] + [y,[z,x]] = 0$,
	\end{enumerate}
	\noindent holds for all $x,y,z \in \mathfrak{g}$.
\end{definition}

\begin{example}[Vector Fiels]
	Let $M$ be a smooth manifold and $U \subseteq M$ open. Then $\mathfrak{X}(U)$ together with $[\>\cdot\>,\>\cdot\>]$ defined in exercise \ref{ex:Lie_bracket_on_vector_fields} is a Lie algebra, called the \bld{Lie algebra of vector fields on $M$}.
\end{example}

\begin{definition}[Lie Algebra Homomorphism]
	Let $\mathfrak{g}$ and $\mathfrak{h}$ be two Lie algebras. A \bld{Lie algebra homomorphism between $\mathfrak{g}$ and $\mathfrak{h}$} is defined to be a homomorphism $L \in \mathrm{L}(\mathfrak{g},\mathfrak{h})$ such that
	\begin{equation*}
		L[x,y] = [Lx,Ly]
	\end{equation*}
	\noindent holds for all $x,y \in \mathfrak{g}$.
\end{definition}


