\section*{Vector Fields}

\begin{definition}[Vector Field]
	Let $M$ be a smooth manifold and $U \subseteq M$ open. A \bld{vector field on $U$} is defined to be a section of the projection $\pi : TU \to U$, where $TU \subseteq TM$. The set of all vector fields on $U$ is denoted by $\mathfrak{X}(U)$.
\end{definition}

\begin{example}[Coordinate Vector Fields]
	Let $M$ be a smooth manifold and $\del[1]{U,(x^i)}$ be a chart on $M$. Define $\frac{\partial}{\partial x^i} : U \to TM$ by
	\begin{equation*}
		\frac{\partial}{\partial x^i}(x) := \frac{\partial}{\partial x^i}\bigg\vert_x.
	\end{equation*}
	It immediately follows from the smoothness criteria for tensor fields \ref{prop:smoothness_criteria_for_tensor_fields} that $\frac{\partial}{\partial x^i} \in \mathfrak{X}(U)$.
\end{example}

\begin{exercise}
	Show that $\mathfrak{X}(U)$ is a $C^\infty(U)$-module. \emph{Hint:} Use the smoothness criteria for tensor fields \ref{prop:smoothness_criteria_for_tensor_fields}.
\end{exercise}

In contrast to arbitrary tensor fields, vector fields can act on smooth functions.

\begin{proposition}
	\label{prop:vector_fields_acting_on_functions}
	Let $M$ be a smooth manifold and $U \subseteq M$ open. Then $X \in \mathfrak{X}(U)$ if and only if the function $Xf : U \to \mathbb{R}$ defined by $Xf(x) := X(x)f$ is smooth for all $f \in C^\infty(V)$, where $V \subseteq U$ is open.
\end{proposition}

\begin{proof}
	Using the smoothness criteria for tensor fields \ref{prop:smoothness_criteria_for_tensor_fields}, we locally write $X = X^i\frac{\partial}{\partial x^i}$, where $X^i$ are smooth functions. Hence
	\begin{equation*}
		Xf = X^i\frac{\partial f}{\partial x^i}
	\end{equation*}
	\noindent which is smooth.\\
	Conversly, suppose that $Xf$ is smooth for any $f \in C^\infty(V)$. Then in particular
	\begin{equation*}
		X(x^j) = X^i\frac{\partial x^j}{\partial x^i} = X^j
	\end{equation*}
	\noindent is smooth.
\end{proof}

We adopt the terminology from \cite[218]{weibel:homological_algebra:1994}.

\begin{definition}[Derivation]
	Let $M$ be a smooth manifold and $U \subseteq M$ open. A \bld{derivation of $C^\infty(U)$} is a linear map $D : C^\infty(U) \to C^\infty(U)$ such that
	\begin{equation*}
		D(fg) = D(f)g + fD(g)
	\end{equation*}
	\noindent holds for all $f,g \in C^\infty(U)$. Denote the set of all derivations of $C^\infty(U)$ by $\Der(U)$.
\end{definition}

\begin{exercise}
	Show that $\Der(U)$ is a $C^\infty(M)$-module.
\end{exercise}

\begin{proposition}
	\label{prop:vector_fields_as_derivations}
	Let $M$ be a smooth manifold and $U \subseteq M$ be open and non-empty. Then $\mathfrak{X}(U) \cong \Der(U)$ as modules over $C^\infty(U)$.
\end{proposition}

\begin{proof}
	Define $\Phi : \mathfrak{X}(U) \to \Der(U)$ by $\Phi(X)(f) := Xf$ using proposition \ref{prop:vector_fields_acting_on_functions}. Moreover, define $\Psi : \Der(U) \to \mathfrak{X}(U)$ by $\Psi(D)(x)(f) := Df$ for all $f \in C^\infty(U)$ again using proposition \ref{prop:vector_fields_acting_on_functions}.
\end{proof}

\begin{remark}
	From now on we will identify vector fields in $\mathfrak{X}(U)$ with derivations $\Der(U)$ by means of proposition \ref{prop:vector_fields_as_derivations}. 
\end{remark}

Proposition \ref{prop:vector_fields_as_derivations} yields a new tool for constructing vector fields.

\begin{exercise}
	\label{ex:Lie_bracket_on_vector_fields}
	Let $M$ be a smooth manifold and $U \subseteq M$ a non-empty open subset. Show that 
	\begin{equation*}
		\sbr[0]{X,Y} := X\circ Y - Y\circ X \in \mathfrak{X}(U)
	\end{equation*}
	\noindent for any $X,Y \in \mathfrak{X}(U)$.
\end{exercise}

